An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-04-28 poly-embed-journal/poly-embed-journal.tex
Adding remaining proofs to section 5

\begin{proposition}\label{prop:tfae-min-rep-nonredundant}
	Let $\R$ be a finite representative set for $L$ eliciting $\Gamma$.
	The following are equivalent:
	\begin{enumerate}
		\item[a.] $\R$ is a minimum representative set for $L$.
		\item[b.] $L|_\R$ is non-redundant.
		\item[c.] For all $r \in \R$, $\Gamma_r$ is full-dimensional, the multiset $\{\Gamma_r : r \in \R\}$ has no duplicate elements, and $\cup_{r\in\R} \Gamma_r = \simplex$.
	\end{enumerate}
\end{proposition}
\begin{proof}[Sketch]
	$(a \implies b)$  
	We show the contrapositive: suppose $L|_\R$ is redundant.
	Then there is a $r,r' \in \R$ such that $\Gamma_r \subseteq \Gamma_{r'}$.
	Then for all $p \in \Gamma_r$, we have $\{r, r'\} \subseteq \Gamma(p)$.
	Therefore, $\R \setminus \{r\}$ still a representative set, so $\R$ is not minimum.

@@

	$(c \implies a)$
	As $\Gamma_r$ is full-dimensional and the multiset $\{\Gamma_r : r \in \R\}$ contains no duplicate elements (that is, there are no $r, r' \in \R$ such that $\Gamma_r = \Gamma_{r'}$), for each $r \in \R$ there must be some distribution $p_r \in \simplex$ so that $\Gamma(p_r) = \{r\}$.
	Thus, $\R \setminus \{r\}$ not a representative set for all $r \in \R$.
	Therefore, $\R$ is minimum.
\end{proof}

@@

\begin{corollary}
	If $\R$ is a minimum representative set for $L$ eliciting $\Gamma$, then $L$ tightly embeds $L|_\R$.
\end{corollary}

\begin{definition}[Trim]\label{def:trim-loss}
	Given an loss $L : \R \to \reals^\Y_+$, we define $\trim(L) = \{L(u) : u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$.
\end{definition}

Observe that if a loss $L : \R \to \reals_+^\Y$ is non-redundant, then $\{L(r) \mid r \in \R\} = \trim(L)$ by applying the definition of non-redundancy.

\begin{corollary}
	$\trim(L)$ is unique.
\end{corollary}
This follows from Proposition~\ref{prop:tfae-min-rep-nonredundant}, as $\trim(L)$ moves from $L$ to remove any non-redundant reports.
$\trim$ removes redundancy of strict subsets (that is, $\Gamma_r \subseteq \Gamma_{r'}$) by the set comprehension, while it removes fully redundant losses ($\Gamma_r = \Gamma_{r'}$) by definition of a set.

\begin{proposition}
	Let $\ell$ be a discrete loss.
	$L$ embeds $\ell$ if and only if $\trim(L) = \trim(\ell)$.
\end{proposition}

>>>>

\begin{proposition}\label{prop:tfae-min-rep-nonredundant}
	Let $\R$ be a finite representative set for $L$ eliciting $\Gamma$.
	The following are equivalent:
	\begin{enumerate}
		\item[a.] $\R$ is a minimum representative set for $L$.
		\item[b.] $L|_\R$ is non-redundant.
		\item[c.] For all $r \in \R$, $\Gamma_r$ is full-dimensional and there is no $r' \in \R'$ such that $\Gamma_{r'}= \Gamma_r$, and $\cup_{r\in\R} \Gamma_r = \simplex$.
	\end{enumerate}
\end{proposition}
\begin{proof}[Sketch]
	$(a \implies b)$  
	We show the contrapositive: suppose $L|_\R$ is redundant.
	Then there is a $r,r' \in \R$ such that $\Gamma_r \subseteq \Gamma_{r'}$.
	Then for all $p \in \Gamma_r$, we have $\{r, r'\} \subseteq \Gamma(p)$.
	Therefore, $\R \setminus \{r\}$ still a representative set, so $\R$ is not minimum.

@@

	$(c \implies a)$
	As $\Gamma_r$ is full-dimensional and there are no $r, r' \in \R$ such that $\Gamma_r = \Gamma_{r'}$, for each $r \in \R$ there must be some distribution $p_r \in \simplex$ so that $\Gamma(p_r) = \{r\}$.
	Thus, $\R \setminus \{r\}$ not a representative set for all $r \in \R$.
	Therefore, $\R$ is minimum.
\end{proof}

@@

\begin{corollary}
	If $\R$ is a minimum representative set for $L$, then $L$ tightly embeds $L|_\R$.
\end{corollary}
\jessie{Add text about how this lets us think about general targets}

\begin{proposition}
	Suppose $\R$ and $\R'$ are minimum representative sets for the loss $L$.
	Then $\{L(r) \mid r \in \R\} = \{L(r') \mid r' \in \R'\}$.
\end{proposition}
\begin{proof}[Sketch]
	It suffices to show $\{L(r) \mid r \in \R\} \subseteq \{L(r') \mid r' \in \R'\}$, and equality will follow by symmetry.
	Consider $r\in \R$, and we want to show $L(r) \in \{L(r') \mid r' \in \R'\}$.
	Since $\R$ and $\R'$ are minimum representative sets, all the level sets must be full-dimensional, and therefore have well-defined interiors (Proposition~\ref{prop:tfae-min-rep-nonredundant}).
	In particular, we must have $\Gamma_r = \Gamma_{r'}$ for some $r' \in \R'$.
	If $L(r) \neq L(r')$, then there would be a distribution $p \in \inter{\Gamma_r}$ such that $\inprod{p}{L(r)} \neq \inprod{p}{L(r')}$. \jessiet{This needs more detail}
	If $\inprod{p}{L(r)} > \inprod{p}{L(r')}$, then $r' \not \in \Gamma(p)$, and $\R'$ is therefore not a representative set.
	Similarly, if the inequality were flipped, we would contradict $\R$ being a representative set.
	Therefore, we must have the losses equal, and $L(r) \in \{L(r') \mid r' \in \R'\}$.
\end{proof}

\begin{definition}[Trim]\label{def:trim-loss}
	Given a loss $L:\R \to \reals_+^\Y$, we define $\trim(L) = \{L(r) \mid r \in \R\}$ given any minimal representative set $\R$ for $L$.
\end{definition}

\begin{proposition}\label{prop:trim-loss-condition}
	Given an loss $L : \R \to \reals^\Y_+$, we have $\trim(L) = \{L(u) : u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$.
\end{proposition}
\begin{proof}[Sketch]
	Suppose $L(u) \in \trim(L)$.
	By Proposition~\ref{prop:tfae-min-rep-nonredundant}, we know $\Gamma_u$ is a full-dimensional level set, and there exists a $p_u$ such that $\{u\} = \Gamma(p_u)$.
	Therefore, $\Gamma_u$ cannot be a subset of any other level set, so $L(u) \in \{L(u) \mid \neq \exists u' s.t. /, \Gamma_u \subsetneq \Gamma_{u'}\}$.

	Now, suppose $L(u) \in \{L(u) \mid \neq \exists u' s.t. /, \Gamma_u \subsetneq \Gamma_{u'}\}$.
	If $L(u) \not \in \trim(L)$, then there is a $u'$ so that $L(u') \in \trim(L)$ and $\Gamma_u \subseteq \Gamma_{u'}$.
	By the set construction, we must have $\Gamma_u = \Gamma_{u'}$, and since $\R$ is a minimum representative set, we know there is a $p_{u'}$ such that $\{u'\} = \Gamma(p_{u'})$.
	Therefore, we must have $u=u'$, so $L(u') = L(u) \in \trim(L)$.
\end{proof}

\begin{proposition}\label{prop:embed-iff-trims-equal}
	Let $\ell$ eliciting $\gamma$ be a discrete loss and $\R$ a minimum representative set for $\ell$.
	$L$ (eliciting $\Gamma$) embeds $\ell$ if and only if $\trim(L) = \trim(\ell)$.
\end{proposition}
\begin{proof}[Sketch]
	$\implies$
	The optimality condition of embedding means $\Gamma_{\varphi(r)} = \gamma_r$ for all $r \in \R$.
	$\R$ a minimum representative set then implies $\varphi(\R)$ is a minimum representative set for $L$.
	Importantly, we have
	\begin{equation*}
	\trim(L) = \trim(L|_{\varphi(\R)}) = \trim(\ell|_\R) = \trim(\ell)~.~
	\end{equation*}
	The outside equalities follow from the sets being minimum representative sets, and the middle one follows from the embedding definition since losses have to match at embedded points.

	$\impliedby$
	First, take $\varphi: r \mapsto u$ if $\ell(r) = L(u)$.
	As these losses match we trivially have the second embedding condition matching losses.
	It just remains to show $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
	\begin{align*}
	r \in \argmin_u \inprod{p}{\ell(u)} &\iff \ell(r) = \min_u \inprod{p}{\ell(u)}\\
	&\iff \ell(r) = \min_{u \in \R} \inprod{p}{\ell(u)} \\
	&\iff L(\varphi(r)) = \min_{u \in \varphi(\R)} \inprod{p}{L(u)} \\
    &\iff L(\varphi(r)) = \min_u \inprod{p}{L(u)} \\
    &\iff \varphi(r) \in \argmin_{u} \inprod{p}{L(u)}
	\end{align*}
\end{proof}
